\vspace{-2.25cm} Multimodal Abnormity-Aware Model\\for Ocular Disease Diagnosis

### 2024-09-07 Paper/Paper.tex
adjust layout
add acknowledgement.

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

	\vspace{-0.7cm}
	\hrule
	\vspace{-0.3cm}
	\section*{Abstract}
	\hrule
	\vspace{0.3cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.

	\vspace{0.2cm}
	{\fontsize{12pt}{12pt}\selectfont \hspace{-0.8cm}\textbf{Keywords: }Multimodal, Deep Learning, Abnormity-Aware, Ocular Diagnosis}
	\vspace{0.3cm}
	\hrule

@@

@@

>>>>

\documentclass{article}
\usepackage{ctex}
\usepackage{hyperref}
\usepackage{geometry}
\usepackage{amsmath}
\usepackage{caption}
\RequirePackage{longtable,multirow,array}
\RequirePackage{booktabs}
\usepackage{booktabs}
\usepackage{multicol}
\usepackage{longtable}
\usepackage{xurl}
\usepackage{booktabs}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{enumitem}
\usepackage{setspace}
\usepackage[style=ieee,sorting=nyt]{biblatex}
\assignrefcontextentries[]{*}
\addbibresource{References.bib}
\geometry{left=1in, right=1in, top=1in, bottom=1in}
\hypersetup{hidelinks}
\hypersetup{bookmarksnumbered=true,
	bookmarksopen=true,
	colorlinks=true,
	linkcolor=black,
	citecolor=blue,
	urlcolor=black}
\usepackage{tikz}
\usepackage{pgfplotstable}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}
\captionsetup{justification=centering}
\captionsetup[figure]{name={Fig.},labelsep=space,labelfont=bf}
\captionsetup[table]{name={Table},labelsep=space,labelfont=bf}
\CTEXoptions[today=old, contentsname=Contents]
\newcommand{\authyear}[1]{\citeauthor{#1} (\citeyear{#1})}
\setmainfont{Arial}

@@

	\hrule
	\vspace{-0.3cm}
	\section*{Abstract}
	\hrule
	\vspace{0.3cm}
	We devise a novel model, the Multimodal Abnormity-Aware Model (MAAM), for assisting ocular disease diagnosis. The MAAM enables input of 2 kinds of ophthalmological images, namely optical coherence tomography (OCT) and color fundus images, and simulates the decision-making process by deducing the disease from abnormities. The model is composed of 2 submodels, the Abnormity Models and the Diagnosis Model, where the Abnormity Models identify 11 OCT abnormities and 8 fundus abnormities, and the Diagnosis Model identifies 12 diseases by integrating features from the former model. In MAAM, we introduce the fusion mechanism, the concept of codominant abnormities and diseases, and the Abnormity-to-Disease Criteria.  The model breaks the black box of complex neural network and expose more interpretable information for the reference of ophthalmologists. And it gets the overall accuracy of 89\% and thus the feasibility is verified.

	\vspace{0.3cm}
	\hrule

	\vspace{0.5cm}
	{\fontsize{12pt}{12pt}\selectfont \hspace{-0.8cm}\textbf{Keywords: }Multimodal, Deep Learning, Abnormity-Aware, Ocular Diagnosis}

@@

	\vspace{0.4cm}

@@

	\section*{Acknowledgement}

	{\setstretch{1.7}

	{\fontsize{12pt}{12pt}\selectfont

	I would like to express my gratitude to my mathematics teacher Mr. Qinglin Xu (徐庆林) for his unrequited guidance and support throughout this research. Mr. Xu's insightful advice on selecting the research topic was invaluable and helped me navigate the initial stages of my work. His constructive feedback on my writing significantly improved the quality and clarity of the paper. Mr. Xu's encouragement and thoughtful suggestions were instrumental in overcoming challenges and refining the direction of this research. His dedication and expertise provided a strong foundation for my work, and I am deeply appreciative of his mentorship and commitment.

	I have been studying one of the ocular diseases, retinitis pigmentosa (RP), for about 2 years since my family folks have this genetic disease.  I had decided 3 to 4 directions on researching the RP, including studying the relationship between the genomes of patients and their symptoms, investigating how genetic factors influence the misfolding of RP-related proteins, and modeling retinal structural damage, etc. Due to lack of laboratory environment in our middle school, Mr. Xu suggested me to pivot my focus onto deep learning area, which can be achieved with certain knowledge and appropriate hardware.  After having sufficient discussion with Mr. Xu., I decided to investigate the model for ocular disease diagnosis.

	When I began to do the study, the first obstacle was that we could not get enough real clinical data.  We communicated with hospitals and institutions, but it was not easy to get approved by authorities at the level of our study.  Therefore, Mr. Xu suggested I use the data from public database and try to build model and verify its feasibility.  I believe this was a key step to make progress and finally I was able to complete this paper.

	Regarding paper writing, Mr. Xu is very experienced and he gave me a lot of suggestions and instructions. I got a lot of help from Mr. Xu when I had difficulties on how to use terminologies, organize the contents and do the background research.  I have been so lucky that I always have Mr. Xu at my side.

	\vspace{0.2cm}
	Again, thank you, Mr. Xu, for your unwavering support and for investing your time and effort in helping me complete this paper.

	}
	}
